---
title: "Gov 50 Final Project"
author: "Yunzhi Liu"
description: "12/12"
output:
  distill::distill_article:
    self_contained: false
editor_options: 
  markdown: 
    wrap: sentence
---

## Project Overview

I use the data from this study:

Nicholas D. Anderson, "Introducing the Warring States Japan Battle Data," International Interactions, Latest articles (2022) <https://doi.org/10.1080/03050629.2023.2149514>

I am combining three datasets from the same study to conduct my regression tests.
These are the variables I am going to mainly look at.

| Name                 | Description                                             |
|:-------------------|:---------------------------------------------------|
| `battle`             | binary variable indicating the occurence of a battle    |
| `battle_id`          | unique numerical identification of a battle             |
| `province`           | name of the province where the battle took place.       |
| `area`               | area of the province                                    |
| `terrain_ruggedness` | the terrain ruggedness of the province                  |
| `forcesA`            | the forces of side A that participated in the battle    |
| `forcesB`            | the forces of side B that participated in the battle    |
| `coalitionA`         | whether side A fought in a formed coalition with others |
| `coalitionB`         | whether side B fought in a formed coalition with others |
| `naval`              | whether the battle was a naval battle                   |
| `siege`              | whether the battle was a siege                          |
| `year`               | The year in which the battle observation was initiated  |

```{r}
library(tidyverse)
library(broom)
library(infer)
library(readr)

rm(warstate)

battledata <- read_csv("~/Desktop/harvard/GOV50/final project potential dataset/WSJBData/WarringStatesJapan_battledataV1.csv")
# View(WarringStatesJapan_battledataV1)

dyadic_data <- read_csv("~/Desktop/harvard/GOV50/final project potential dataset/WSJBData/WarringStatesJapan_diffusiondata_dyadic.csv")

monadic_data<- read_csv("~/Desktop/harvard/GOV50/final project potential dataset/WSJBData/WarringStatesJapan_diffusiondata_monadic.csv")

battledata <- rename(battledata, province_name = province)


warringstate <- merge(battledata, monadic_data, by.x = c('year', 'province_name'), by.y = c('year', 'province'), all.x = TRUE)

```

I loaded the data and joined the three datasets into one.
Now, let's begin.

First, let's look at the data.

We can see that there are 2889 unique `battle_id`, which means in total there were 2889 unique battles that took place during Japan's Warring-States period, according to this dataset.

However, once we join the datasets for a comprehensive view, there appears 6875 lines of observations.
This is because for some battles, there are different historically noteworthy leaders on either side, so the author decides to repeat the battle objects to include all the leaders' names.

For my purpose, the names of these leaders do not really matter.
Therefore, I will drop the names to keep one entry for each battle.
I will also do several other column dropping to make the data more workable, specifically the day of battle, the month, the source of information.

```{r}
warringstate <- warringstate |>
  select(-sideA, -sideB, -location, -day, -day2, -month, -month2, -source) |>
  distinct(battle_id, .keep_all = TRUE)
```

Now we have a data set with 2889 unique battles!

Now, let's look at the data again, and try to figure out what is going on in Japan during this time.

Because this is historical data, it is very non-exhaustive (with many NAs) and sometimes vague (estimated or ranged numbers).
Such is the limitation of digital humanities (or, if you count history as social sciences, you should be having a hard time understanding the reality of data availability after GOV50 as I am now).

Therefore, we need to first look at the data, do some cleaning (I am converting several variables into binary variables), before attempting at any regression.

**Descriptive: Getting familiar with Japan's Warring State Battles**

1.  *Inland or Near-Shore*

Since the frequency of battles in each provinces and regions have been analyzed by the author himself already, I am now interested, instead, in learning about whether battles took place more often in purely inland provinces or near-shore provinces.

I am curious about this because of Japan's geographical feature as an archipelago.
I therefore wonder if we can see a significant difference in the total number of conflicts taking place in purely inland locations versus near shore provinces, even if not naval battles.

```{r}
#I am defining inland and near shore provinces according to the Japanese version of the Warring-state Japan map, accessed through https://sengokumap.net/province-map/province-map/

near_shore_provinces <- c("yamashiro", "ise", "harima", "hizen", "kii", "settsu", "bizen", "aki", "chikuzen", "bingo", "buzen", "nagato", "suo", "awa1", "izu", "tsushima", "izumo", "iki", "musashi", "toutoumi", "osumi", "satsuma", "sagami","tosa", "houki", "ecchu", "higo", "hyuuga", "sanuki", "bungo", "iyo", "oki", "noto", "awa2", "awaji", "sado")

inland_provinces <- c("yamato", "tanba", "shinano", "mimasaka", "oumi", "tajima", "kaga", "kawachi", "mino", "owari", "echizen", "kai", "tango", "bicchu", "mutsu", "shimotsuke", "izumi", "shimousa", "kazusa", "kouzuke", "chikugo", "inaba", "hitachi", "echigo", "mikawa", "iga", "wakasa", "dewa", "iwami", "hida", "suruga")

```

```{r}
#create new variables
warringstate <- warringstate |>
  mutate(
    geography = case_when(
    province_name %in% inland_provinces ~ "inland",
    province_name %in% near_shore_provinces ~ "shore"),
    battle_geography = if_else(naval == 1, "Naval Battle", "Land Battle"),
    naval = as.factor(naval))

#count the total number of battles in inland provinces and shore provinces
tb_inlandshore <- warringstate |>
  group_by(geography) |>
  count() |>
  drop_na()
knitr::kable(tb_inlandshore)

#plot the number of battles in inland provinces and shore provinces over years
landshore_plot <- warringstate |>
  mutate(shore = if_else(geography == "shore", 1, 0)) |>
  filter(!is.na(shore)) |>
  group_by(year, shore) |>
  summarize(count = n(), .groups = 'drop') |>
  ggplot(aes(x = year, y = count)) +
  geom_point() +
  geom_smooth(na.rm = FALSE) +
  facet_wrap(~ shore, labeller = as_labeller(c('0' = 'no. of battles in inland provinces', '1' = 'no. of battles in shore provinces')))
landshore_plot
```

```{r}
# Count battles per year for each geography
xxxx
```

Analysis:

We see a significant rise in numbers of battles after the 1550s, and the number of battles peaking at around 1580s, both in inland provinces and shore provinces.

We also see a much higher number of shore-province battles in the 1450s (the beginning of the warring state period), which may be an indicator that in the beginning of the time period, these battles were not so politically charged and complex in their reasons for taking place: instead, people fought simply out of necessity, for resources, which mostly came from the sea in the case of premodern Japan.
It may also be reflect the development of inland fighting technologies from the 1450s to the 1500s, which results in a proportional rise in inland battles (a proportional decrease in near-shore battles.)

(Side Note: I decided to not use the area plot to demonstrate the proportions because there are 124 battles which took place in provinces unknown (aka, geography = NA).
Although the number is comparatively small and should not significantly impact the general trends as shown here in these smoothed-lines, they do play a role if I were to make an area plot.
)

This lead to a question: is the more significant increase in number in inland provinces due to the technical advancement for land battle?

2.  *Technical advancement in battle: Calvary*

Let's look at the dataset again and see how to extract the information whether a battle has cavalry involved.

```{r}
forces_data_type <- unique(c(warringstate$forcesA, warringstate$forcesB)) |>
  tibble() 
knitr::kable(forces_data_type, caption = "Types of Forces in this data")

```

We can see that this variable is categorical, with a diversity of information.\
We are mainly interested in those that has "cavalry" involved here.
I am using the "str_detect" function to create a new variable `cavalry` denoting whether a battle has cavalry involved, as well as `cavalryA`, whether side A has cavalry, and `cavalryB`, whether side B uses cavalry.

```{r}
#extracting information about cavalry involved
warringstate <- warringstate |>
  mutate(cavalryA = if_else(str_detect(forcesA, "cavalry"), 1, 0),
         cavalryB = if_else(str_detect(forcesB, "cavalry"), 1, 0),
         cavalry = if_else(cavalryA == 1|cavalryB == 1, 1, 0))

#counting the number of cavalry involved battles in total
cavalrytotal <- warringstate |>
  count(cavalry == 1)
knitr::kable(cavalrytotal)

#plotting the total number of cavalry battles
cavalry_battle <- warringstate |>
  filter(cavalry == 1) |>
  group_by(year)|>
  summarize(count = n()) |>
  ggplot(aes(x = year, y = count))+
  geom_point() +
  geom_smooth(na.rm = FALSE) +
    labs(
    title = "Number of Cavalry Battles",
    x = "Year",
    y = "No. of Cavalry Battles"
  )


#proportion of cavalry-involved battle each year
total_prop_cavalry <- warringstate |>
  group_by(year) |>
  summarize(
    total_battles = n(), 
    cavalry_battles = sum(cavalry, na.rm = TRUE), 
    proportion_cavalry = cavalry_battles / total_battles
  ) |>
  filter(proportion_cavalry > 0)

total_prop_cavalry_plot <-
  ggplot(total_prop_cavalry, aes(x = year, y = proportion_cavalry)) +
  geom_point() + geom_smooth() +
   scale_y_log10() +
  labs(
    title = "Proportion of Cavalry Battles Over Years",
    x = "Year",
    y = "Proportion of Cavalry Battles"
  )

cavalry_battle + total_prop_cavalry_plot
```

Analysis:

The proportion of cavalry battles is so small over all recorded years, which makes me less confident to interpret the first "number of cavalry battles over years" plot as precisely representative of the history.

However, the smooth line in the proportion plot is indicative of the general trend of cavalry use over the years.
The observation of the sharp rise in cavalry proportion from the 1450s to the 1500s, matches with our assumption that the rise in cavalry......

*#Road Battle*

Anderson in his paper narrates that, "`adjacent_battle` simply indicates whether a province sharing a land border with a given province experienced conflict within the past 24 months; `road_battle` adds the condition that this adjacent province also shares a major road with the province in question." (Anderson, 7)

This inspires me to compare the numbers of `adjacent_battle` and `road_battle` overtime, to see if there is any divergent in the change in battle numbers that may indicate an improvement in road infrastructure correlated to a rise in road battle numbers.

```{r}
battle_summary <- warringstate |>
  group_by(year) |>
  summarize(road_battles = sum(road_battle, na.rm = TRUE),
            adjacent_battles = sum(adjacent_battle, na.rm = TRUE))

road_vs_adjacent <- battle_summary |>
  ggplot(aes(x = year)) +
  geom_line(aes(y = road_battles, color = "Road Battles"), size = 1.2, alpha = 1) +
  geom_line(aes(y = adjacent_battles, color = "Adjacent Battles"), size = 1.2, alpha = 0.8) +
  scale_color_manual(values = c("Road Battles" = "blue", "Adjacent Battles" = "indianred1")) +
  labs(title = "Road Battles vs Adjacent Battles",
       x = "Year", y = "Number of Battles",
       color = "Battle Type") 
road_vs_adjacent

```

Analysis: From this plot, we can observe that over time there are similar trends in the frequency of battles taking place where major road connections exist and simply with adjacent states.
It is therefore hard to conclude that an improvement in road infrastructure correlated to a rise in road-specific battles, since adjacent battle numbers always rise and fall together with the number of road battles.

*#Cavalry and terrain ruggedness*

Here I am looking at whether the usage of cavalry is correlated to the terrain ruggedness of the province of battle, holding constant other variables such as `road_battle` (whether the battle was on a major road instead of between adjacent provinces), the `area` (size of the province), `year`, and `neighbors` (how many neighboring provinces was this province adjacent to.)

```{r}
cavalry_terrain <- 
  lm(cavalry ~ terrain_ruggedness + road_battle + area + year + neighbors, data = warringstate)
summary(cavalry_terrain)
```

**Regression**

*#Whether a battle tends to take place more often on rugged or none rugged terrains, (holding constant year, etc.)*

```{r}
battle_likelyhood <- lm(battle ~ terrain_ruggedness + road_battle + area + year + neighbors, data = warringstate)
summary(battle_likelyhood)
```

*#Whether VictoryA is correlated to the use of cavalry in the battle, whether either side is joined by coalition, and who initiated the fight.*

```{r}
victory_a <- lm(victoryA ~ cavalryA + cavalryB + coalitionA + coalitionB + initiatorA, data = warringstate)
summary(victory_a)
```

*#Whether the number of draws are correlated to the use of cavalry (holding constant coalition, etc.)*

```{}
```

*#Whether the number of total casualties is correlated to the usage of cavalry (Note that this result is not so reliable, because there are could be missing data of casualties for battles on either or both sides.)*

```{r}
casualties_data_type <- unique(c(warringstate$casualtiesA, warringstate$casualtiesB)) |>
  tibble() 
knitr::kable(casualties_data_type, caption = "Types of Casualties in this data")
```

Analysis & Interpretation:
